---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(here)
```

```{r}
here()
```


```{r}
sales_2016 <- read_csv("raw_data/sales-2016-with-ratings.csv")
```

```{r}
sales_2016
```

```{r}
names(sales_2016)
```

I wanted to check all the variable names. They are in capitals so I want to lose the capitals so I will use the clean_names function from janitor package:

```{r}
sales_clean_2016 <- clean_names(sales_2016)
```

```{r}
glimpse(sales_clean_2016)
```

O want to check for missing variables and n/a so I do this through summary function.

```{r}
summary(sales_clean_2016)
```

Things I note from the summary:

year_of_release is character class which is odd. Is it a relevant variable to answer the questions? I think for plotting time series that it could be so I would want to change the year to an integer.

na_sales is North American sales
eu_sales is European
jp_sales is Japan
other_sales is rest of world
global_sales is the sum of all the others



```{r}
sales_clean_2016 %>% 
  ggplot(aes(x = name, y = global_sales)) +
  geom_point()
```

So it would appear that there is one outlier that done much better than the rest.
Let's try and find out who that is:

```{r}
sales_clean_2016 %>% 
  arrange(desc(global_sales))
```

```{r}
boxplot(sales_clean_2016$global_sales)
```












